Think deep for reef resilience

### 2025-08-07 paper/paper_draft.qmd
Update subsection header
@eco-ben I changed my mind - the section does describe some methodological aspects so moved this back to under Methods.

## Modelling context

@@

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points). The green polygon represents the Far Northern management area,
the yellow polygon represents the Cairns/Cooktown management area, the pink polygon
represents the Townsville/Whitsunday management area and the blue polygon represents the
Mackay/Capricorn management area. The centroid of each reef is represented as a point for
visual clarity, and is coloured according to its GBRMPA reefal bioregion. An annotation
represents the approximate location of the Australian Institute of Marine Science Townsville
site at Cape
Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map}

## Degree Heating Week Trajectories

>>>>

## Reef representations

@@

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points). The green polygon represents the Far Northern management area,
the yellow polygon represents the Cairns/Cooktown management area, the pink polygon
represents the Townsville/Whitsunday management area and the blue polygon represents the
Mackay/Capricorn management area. The centroid of each reef is represented as a point for
visual clarity, and is coloured according to its GBRMPA reefal bioregion. An annotation
represents the approximate location of the Australian Institute of Marine Science Townsville
site at Cape
Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map
alt="Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all considered reefs (points). The green polygon represents the Far Northern management area, the yellow polygon represents the Cairns/Cooktown management area, the pink polygon represents the Townsville/Whitsunday management area and the blue polygon represents the Mackay/Capricorn management area. The centroid of each reef is represented as a point for visual clarity, and is coloured according to its GBRMPA reefal bioregion. An annotation represents the approximate location of the Australian Institute of Marine Science Townsville site at Cape Cleveland."}

## Degree Heating Week trajectories
